---
title: "LoadEducation"
author: "Alex Frye"
date: "June 12, 2016"
output: md_document
---

The Education data are are found [here](https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv).

**Data Notes**

*"The World Bank EdStats All Indicator Query holds around 3,000 internationally comparable indicators that describe education access, progression, completion, literacy, teachers, population, and expenditures. The indicators cover the education cycle from pre-primary to vocational and tertiary education."* [Data.worldbank.org](http://data.worldbank.org/data-catalog/ed-stats)

Lets load this data from it's source if you do not already have this data file in the DataLoad Directory. 

```{R DownloadEducation.csv}
setwd(DataLoad)

##Only download the file fresh if the file does not exist
if (file.exists("Education.csv") ==FALSE) {
  ## Download CSV File
  url <-"https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv"
  download(url, destfile = "Education.csv")
}  

#Verify file exists in DataLoad Directory
list.files()
```

If the File's Data SHA1 HASH value does not match original research, lets re-load it.

```{r VerifySHA1_and_LoadEducation}
##Load Education.csv into EducationRaw data.frame
EducationRaw <- read.csv("Education.csv",stringsAsFactors = FALSE,header = TRUE)

## Ensure that the Education.csv file's data sha1 HASH value matches that of original research
## Define Data SHA1 HASH
SHAHASHEducation <- digest(EducationRaw, algo="sha1")
 
## If file's data does not match original research, download file fresh and check again
if (SHAHASHEducation != "aa8a8e7da032757672d3522d645d89f128a98cb2") {
  url <-"https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FEDSTATS_Country.csv"
  download(url, destfile = "Education.csv")
  
  EducationRaw <- read.csv("Education.csv",stringsAsFactors = FALSE,header = TRUE)
  
  ## Define new Data SHA1 HASH
  SHAHASHEducation <- digest(EducationRaw, algo="sha1")
  
  ## If file's data still does not match, STOP BUILD WITH ERRORS
  if (SHAHASHEducation != "aa8a8e7da032757672d3522d645d89f128a98cb2") {

  stop("File SHA1 HASH Value does not match original research. Valid SHA1 HASH value of data = \"aa8a8e7da032757672d3522d645d89f128a98cb2\"")

  }
}

```

Lets review the first and last 10 records of this file:

```{r HeadEducationRaw}
formattable(head(EducationRaw,10))
formattable(tail(EducationRaw,10))
```
