---
title: "README"
author: Alex Frye
output: 
  md_document
---

```{r DeclarePath, echo=  FALSE}
##Change this path per your project root directory on your machine if you wish to regen the README.html file
DefaultDir<-"D:/Documents/School/SMU/2016 Summer/MSDS 6306 - Into to Data Science/2DS Printouts/Unit 6/MSDS6306_Week6CaseStudy"

RResourcesDir<-paste(DefaultDir,"/RResources",sep = "")
```

##Assignment Definition
*	Deliverable: Markdown file uploaded to GitHub containing the following 
*	Introduction to the project. The introduction should not start with “For my project I …”. The introduction needs to be written as if you are presenting the work to someone who has given you the data to analyze and wants to understand the result. In other words, pretend it’s not a case study for a course. Pretend it’s a presentation for a client.
*	Code for downloading, tidying, and merging data in a R Markdown file.
*	Brief explanations of the purpose of the code. The explanations should appear as a sentence or two before or after the code chunk. Even though you will not be hiding the code chunks (so that I can see the code), you need to pretend like the client can’t see them.
*	Code to answer the five questions above (plus the answers) in the same R Markdown file.
*	Clear answers to the questions, including interpretation of the plots.
*	Conclusion to the project. Summarize your findings from this exercise.
*	The file must be readable in GitHub – 5 points off if I have to download the file to read it! In other words, don’t forget to keep the md file!!


##FILE TREE STRUCTURE DEFINED
```{r Twee, echo = FALSE}
setwd(DefaultDir)
source(paste(RResourcesDir,"/twee.R",sep = ""))
twee()
```

**NOTE:** Project Deliverable File Located: "~/Paper/AFrye_Week6CaseStudy.MD"

##PROJECT REPRODUCIBILITY INSTRUCTIONS

1. Regenerate README (If Project File Structure Changes)
    + Open README.RMD located inside Project Root
    + Modify DefaultDir input to your Project's Root Directory Path
    + Knit README.Rmd
2. Regenerate AFrye_Week6CaseStudy.MD
    + Open AFrye_Week6CaseStudy.RMD
    + Modify DefaultDir input to your Project's Root Directory Path
    + Ensure all required R Packages are installed on your machine. Uncomment any needed Install.Packages code lines
    + Knit AFrye_Week6CaseStudy.RMD
