---
title: "Afrye_Week6CaseStudy"
author: "Alex Frye"
date: "June 12, 2016"
output: md_document
---

```{r DefineDirectory, include=FALSE}
##Change this path per your project root directory on your machine if you wish to regen the RollingSales_Manhattan_Paper.HTML file
DefaultDir<-"D:/Documents/School/SMU/2016 Summer/MSDS 6306 - Into to Data Science/2DS Printouts/Unit 6/MSDS6306_Week6CaseStudy"

DataLoad<-paste(DefaultDir,"/DataLoad",sep = "")
DataCleanup<-paste(DefaultDir,"/DataCleanup",sep = "")
DataAnalysis<-paste(DefaultDir,"/DataAnalysis",sep = "")

```




#Introduction

Our partners at "The World Bank" have captured and have provided us with GDP Ranking and Education statistics of countries across the world. These datasets are important assets to answering key questions for our stakeholders. Although we have been provided the data from "The World Bank", there are several steps needed to be taken before analysis can begin on the data. In the below sections, we will walk through loading and cleaning the datasets provided to us. Once we are comfortable with the data, we will dive into our analysis and answer 5 core questions recently asked by our stakeholders.

###Required Packages

This RMD requires the following R packages to run:
* downloader
* digest
* formattable
* plyr
* ggplot2
* dplyr

If you do not currently have installed any of these packages, please uncomment the install.packages lines below before knitting this file.

```{R Install_Load_Pkgs}
#install.packages("downloader")
#install.packages("digest")
#install.packages("formattable")
#install.packages("plyr")
#install.packages("ggplot2")
#install.packages("dplyr")

library(downloader)
library(digest)
library(formattable)
library(plyr)
library(ggplot2)
library(dplyr)

```

#Data Load

The Data utilized for this study is sourced from data.worldbank.org (specific file download links to be provided below). The below sections will walk through loading the data and verifying that the data values match the original research files. 

###Products Data Load
``` {r data, child = paste(DataLoad,"/LoadProduct.rmd",sep = "")}
```

###Education Data Load
``` {r data, child = paste(DataLoad,"/LoadEducation.rmd",sep = "")}
```


#Data Cleanup

Data cleanup is imperative to any data analysis. In our precursory view into header/footer records, we can tell there are several items needing to be cleaned across the two datasets. The following sections will walk through cleaning the data to prep for analysis.

###Products Data Cleanup
``` {r data, child = paste(DataCleanup,"/CleanProduct.rmd",sep = "")}
```

###Education Data Cleanup
``` {r data, child = paste(DataCleanup,"/CleanEducation.rmd",sep = "")}
```

#Data Analysis & Questions

Now that we have Cleaned and Merged our data, we may begin our analysis. Stakeholders have requested answers to 5 core questions:

###Question 1
####Match the data based on the country shortcode. How many of the IDs match? 
``` {r data, child = paste(DataAnalysis,"/Question1.rmd",sep = "")}
```

###Question 2
####Sort the data frame in ascending order by GDP rank (so United States is last). What is the 13th country in the resulting data frame? 
``` {r data, child = paste(DataAnalysis,"/Question2.rmd",sep = "")}
```

###Question 3
####What are the average GDP rankings for the "High income: OECD" and "High income: nonOECD" groups? 
``` {r data, child = paste(DataAnalysis,"/Question3.rmd",sep = "")}
```

###Question 4
####Plot the GDP for all of the countries. Use ggplot2 to color your plot by Income Group.
``` {r data, child = paste(DataAnalysis,"/Question4.rmd",sep = "")}
```

###Question 5
####Cut the GDP ranking into 5 separate quantile groups. Make a table versus Income.Group. How many countries are Lower middle income but among the 38 nations with highest GDP?
``` {r data, child = paste(DataAnalysis,"/Question5.rmd",sep = "")}
```

#Conclusion

In analyzing our GDP and Education data for countries around the world, we had to go through several steps in order to start analyzing our data. Data cleanup processes were performed to remove NA/Blank values, remove unwanted miscellaneous text, and ensure our variable types are classified correctly. This process is imperitive to providing accuracy in analysis!!

With the Cleaned Data, we answered some core questions from our stakeholders. We were provided with 189 countries containing data in both GDP and Education metrics. Of those 189 countries, St. Kitts and Nevis (KNA) was identified as the 13th lowest ranked by USD. We also reviewed the average GDP Rankings/USDollars by IncomeGroup. A visual was presented to display GDP(in dollars) by country, highlighting the differences in Income Groups. Finally, we were able to identify the 5 countries which are both classified as Lower middle income, and fall under the top 20% GDP ranking.
